Slightly Positive Correlation Between Racialization, Gendering and Police Strip Searches in the Toronto Municipal, 2020-2021

### 2024-01-26 outputs/paper/paper.qmd
further edit graphs and final polish of paper

Then, @fig-race-strip-search illustrates the percentage of strip searches among different racial groups in Toronto from 2020-2021. Observably, while being the the major population group in Toronto, people of white racial roots aren't the most strip searched. Rather, it's the racialized population of Toronto like black and Indigenous people that are being strip searched by police, at respectively, 16% and 14% each. This hints at the possibility of strip search being more racialized than it seems, targeting minority groups in Toronto due to racial biases. Moreover, examining @fig-race_strip_search_separate, 2434 out of 17526 black people are strip searched in Toronto from 2020 to 2021, making them overrepresented despite their small population make-up. Once more, this emboldens the racialized nature of police strip search.

@@

Regarding @fig-reasons-gender, intriguingly, the graph calls into question of the above data confirming how males are slightly more likely to be strip searched compared to females when they're arrested. However, when intersected with data like the total number of reasons attributed strip searches, there appears to be a trend of females being more frequently strip searched when there are a smaller number of reasons--0-2 reasons--regarding their actions at the time of arrests. Specifically, this can translate to the fact that police more readily strip-search females compared to males even if the severity of their actions may not necessitate strip searching. Yet again, this hints at the potential of strip searching being sexually motivated and gendered, especially when there are mostly male police officers in Toronto [@policeStats] and where strip searching is notoriously regarded as a guise for sexual assault [@stripSearchNSW].

>>>>

Then, @fig-race-strip-search illustrates the percentage of strip searches among different racial groups in Toronto from 2020-2021. Observably, while being the the major population group in Toronto, people of white racial roots aren't the most strip searched. Rather, it's the racialized population of Toronto like black and Indigenous people that are being strip searched by police, at respectively, 16% and 14% each. This hints at the possibility of strip search being more racialized than it seems, targeting minority groups in Toronto due to racial biases. Moreover, examining tbl-race-strip-search, 2434 out of 17526 black people are strip searched in Toronto from 2020 to 2021, making them overrepresented despite their small population make-up. Once more, this emboldens the racialized nature of police strip search.

@@

Regarding @fig-reasons-gender, intriguingly, the graph calls into question of the above data confirming how males are slightly more likely to be strip searched compared to females when they're arrested. However, when intersected with data like the total number of reasons attributed to strip searches, there appears to be a trend of females being more frequently strip searched when there are a smaller number of reasons--0-2 reasons--regarding their actions at the time of arrests. Specifically, this can translate to the fact that police more readily strip-search females compared to males even if the severity of their actions may not necessitate strip searching. Yet again, this hints at the potential of strip searching being sexually motivated and gendered, especially when there are mostly male police officers in Toronto [@policeStats] and where strip searching is notoriously regarded as a guise for sexual assault [@stripSearchNSW].
